---
title: "Template"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    code_download: true
    collapsed: yes
    keep_md: yes
    number_sections: yes
    smooth_scroll: no
    toc: yes
    toc_depth: 2
    toc_float: yes
  word_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---
\def\blue{\color{blue}}


```{r setup, include=FALSE} 
# Loading required libraries
list.of.packages <- c("tidyverse", "haven", "here", "kableExtra")

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages, repos= "http://cran.cnr.berkeley.edu/")

lapply(list.of.packages, library, character.only = TRUE)

knitr::opts_knit$set(root.dir = here())
knitr::opts_chunk$set(echo = TRUE)

print_code <- TRUE
``` 


```{r parameters, echo=print_code}
# Do not run data set on git/github until privacy has been cleared
################
##### Data  
################
################
##### Research
################
################
##### Guess work   
################
################
#####  Notes:
################
### Source ---->  Input ----> Model ----> Policy Estimates (output)
###  (_so)        (_in)       (_mo)        (_pe)
### values      functions   functions      values
###             & values    & values
### arguments in functions should used "_var" and functions should "_f"
#invisible( list2env(call_params_f(),.GlobalEnv) )
```

# Introduction
Summary of the issue and introduction to the policy analysis being conducted. 

The goal of this analysis is to provide the best empirical information for policy makers debating the implemention of "x" policy. This document describes all the analytical steps required to reproduce the analysis, and displaying the actual computer code use in each step. In addition to this report, the reader can find all the materials to reproduce the findings presented here in "github". The main output, presented in the results section of this report, can also be explored interactively for different assumptions.

## Source Information for data + analytical methods

## Key policy estimates for policy makers  
```{r}
#my thoughts: should we forefront the conclusions before the methodology?
```

```{r final-output}
```

# Methodology

Present explanation of how the analysis is to be performed, what factors are looked at, etc.

## Main Equation (the model)

\begin{equation}
y = f(x)
\label{eq:1}
\tag{1}
\end{equation}

```{r test, eval=FALSE}
# - inputs: 
# - outputs: 
chunk_test <- function(){
############################################################################### 
###############################################################################  
  
    somefunction_f <- function(something_var = something_default) {
        something_var
    }
    
############################################################################### 
###############################################################################  
    return(list("somefunction_f" = delta_earnings))    # Try to return only functions
}
invisible( list2env(chunk_test(),.GlobalEnv) )

##### Execute values of the functions above when needed for the text:
somefunction_in <- somefunction_f()
```

## Sub components:

### Component 1 ("$r$")

This is the formula used to calculate component 1[^1]

\begin{equation}
r = X \times \lambda_1  + (1 - X) \times \lambda_2
\label{eq:2}
\tag{2}
\end{equation}

```{r comp1,  echo=print_code, eval=FALSE}
# - inputs: factors of r
# - outputs: r value
chunk_r <- function(){
###############################################################################
###############################################################################  

    r_function_f <- function(r_input1_var = input1 , r_input2_var = input2) {  
        r_value = r_input1_var - r_input2_var
        return(list("r_value" = r_value))
    }

###############################################################################
###############################################################################  
    return(list("r_function_f" = r_function_f))
}

invisible( list2env(chunk_r(),.GlobalEnv) )
r_parameter <- as.numeric( r_function_f() )
```

### Component 2 ("$q$")

This is the formula used to calculate component 2[^2]

\begin{equation}
q =  \text{input} \times \alpha_0 (1 + g)^{X}(1 + \hat{\beta_1} X + \hat{\beta_2} X^2)
\label{eq:3}
\tag{3}
\end{equation}

```{r comp2,  echo=print_code, eval=FALSE}
# - inputs: factors of q
# - outputs: q value
chunk_q <- function(){
###############################################################################
###############################################################################  

    q_function_f <- function(q_input1_var = input1 , q_input2_var = input2) {  
        r_value = (q_input1_var * q_input2_var)^2
        return(list("q_value" = q_value))
    }

###############################################################################
###############################################################################  
    return(list("q_function_f" = q_function_f))
}

invisible( list2env(chunk_q(),.GlobalEnv) )
r_parameter <- as.numeric( q_function_f() )
```
# Main results
```{r main-results,  echo=print_code}
# - perform the calculations to achieve final results

results_table <- data.frame("results1" =   c("results", NA,
                                             NA) ,
                        "results2" =  c(NA, "results", NA),
                        "results3" = c("results", NA,
                                             "results"),
                        
                        row.names = c("situation1", "situation2", "situation3"))

kable(results_table, caption = "Table Caption") %>%
  kable_styling("striped", full_width = F)
```


# Montecarlo simulations  
```{r,  echo=print_code}
# Draws
# Compute inputs
# Compute model
# Run sims
```

# Sensitivity Analysis  

# Conclusions

# References


[^1]: Notes of referenced section


[^2]: Notes on referenced section