---
title: "Dynamic Document for Fiscal Impacts of Deworming"
output:
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---
\def\blue{\color{blue}}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Who are the policy makers?
 - Ministries of Health, Education and Finance. 

## What is the relevant output that should be used to inform them?
 - NPV
 
 Proposed output: 
```{r sample-output, echo=FALSE, warning=FALSE, message=FALSE}
set.seed(1234)
library(tidyverse)

ggplot() +
  geom_density(aes(x = rnorm(1000, mean = 1),
                   alpha = 1/2), bw=.11, kernel = "gau") +
  geom_vline(xintercept = c(0, 1), col="blue") +
  coord_cartesian(xlim = c(-3,3)) +
  scale_x_discrete(limits = c(0,1))  +   
  guides(alpha = "none", colour="none") +
  labs(y = NULL,
       x = "NPV" ,
       title = "Figure 1: Distribution NPV of Fiscal Impacts of Deworming")+
  theme(axis.ticks = element_blank(), axis.text.y = element_blank())



```
 




## Main Equation (the model)


\begin{equation}
NPV =  \sum_{\gamma} N_{\gamma} \left[ 
\tau \sum_{t=0}^{50} \left( \frac{1}{1 + r}\right)^{t} w_{t} 
\left( \lambda_{1, \gamma} + \frac{p \lambda_{2, \gamma}}{R} \right) - 
K \sum_{t=0}^{50} \left( \frac{1}{1 + r}\right)^{t} \Delta \overline{E}_{\gamma t}(S1,S2)
\right] - \left( S_{2}Q(S_{2}) - S_{1}Q(S_{1}) \right)
\label{eq:1}
\tag{1}
\end{equation}


```{r npv}
# Gamma is used to index gender. 

npv <- function(n_female, n_male, periods, 
                interest_r, wage, lambda1_male,lambda_1_female, 
                saturation, coverage, cost_of_schooling, delta_ed_male, 
                delta_ed_female, lambda2_male, lambda2_female, 
                s1, q1, s2, q2, periods) {

  sum( n
    ) 
    
  \sum_{\gamma} N_{\gamma} \left[ 
\tau \sum_{t=0}^{50} \left( \frac{1}{1 + r}\right)^{t} w_{t} 
\left( \lambda_{1, \gamma} + \frac{p \lambda_{2, \gamma}}{R} \right) - 
K \sum_{t=0}^{50} \left( \frac{1}{1 + r}\right)^{t} \Delta \overline{E}_{\gamma t}(S1,S2)
\right] - \left( S_{2}Q(S_{2}) - S_{1}Q(S_{1}) \right)
  
}
```

