---
title: "Dynamic Document for Fiscal Impacts of Deworming"
output:
  html_document:
    code_folding: hide
  word_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---
\def\blue{\color{blue}}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r parameters}
# chante _vals to _so
#############
##### Data  
#############
gov_bonds_so <- 	0.1185	     #Kenyan interest on sovereign debt - Central Bank of Kenya
inflation_so <-  0.02          #Kenyan inflation rate - World Bank Development Indicators
wage_ag_so <- 	11.84	         #Mean hourly wage rate (KSH) - Suri 2011
wage_ww_so <- 	14.5850933     #Control group hourly wage, ww (cond >=10 hrs per week) - Table 4, Panel B
profits_se_so <- 1766          #Control group monthly self-employed profits - Table 4, Panel A  FIX: MOST REFERENCES FROM TABLE 4 ARE TABLE 3
hours_se_cond_so <- 38.1       #Control group weekly self-employed hours, conditional on hrs >0 - Table D13, Panel D
hours_ag_so <- 8.3             #Control group hrs per week, agriculture - Table 4, Panel D
hours_ww_so <- 6.9             #Control group hrs per week, working for wages - Table 4, Panel B
hours_se_so <- 3.3             #Control group hrs per week, self-employment - Table 4, Panel A
ex_rate_so <- 85               #Exchange Rate - Central Bank of Kenya
growth_rate_so <- 1.52/100     #Per-capita GDP growth, 2002-2011 (accessed 1/29/13) -	World Bank - see notes
coverage_so  <- 0.681333333    # (R) Fraction of treated primary school students within 6 km - from W@W - see note
tax_so <- 0.16575              #ADD INFO
unit_cost_local_so <- 43.66    #Deworm the World
years_of_treat_so <- 2.41      #Additional Years of Treatment - Table 1, Panel A
#############
##### Research
#############    
lambda1_so <- c(3.49, 0)       #Hrs per week increase for men and women CONFIRM
lambda2_so <- 10.2             #Externality effect (proportional) - Table 3, Panel B
q_full_so <- 0.75              #Take up rates with full subsidy. From Miguel and Kremmer (2007)
q_zero_so <- 0                 #Take up rates with zero subsidy. From Miguel and Kremmer (2007)
delta_ed_so <- c(-0.00176350949079451, 0.00696052250263997, 0.0258570306763183,     # (Delta E) Additional direct seconday schooling increase (from Joan)
                    0.0239963665555466, 0.027301406306074, 0.0234125454594173,
                   0.0279278879439199, 0.00647044449446303, 0.00835739437790601)                                     
delta_ed_so <- cbind(delta_ed_so, 1999:2007)
delta_ed_ext_so <- c(-0.0110126908021048,	0.0140448546741008,	-0.0034636291545585,  #Additional externality secondary schooling increase (from Joan)
                       0.0112940214439477,	0.0571608179771775,	-0.0560546793186931,
                       0.0558284756343451,	0.1546264843901160,	0.0055961489945619)
delta_ed_ext_so <- cbind(delta_ed_ext_so, 1999:2007)    
#############
##### Guess work   
#############
periods_so <- 50               #Total number of periods to forecast wages
time_to_jm_so <- 10            #Time from intial period until individual join the labor force
coef_exp_so <- c(0, 0)         #Years of experience coefficients (1-linear, 2-cuadratic)	- see notes
teach_sal_so <- 5041           #Yearly secondary schooling compensation	5041 - from ROI materials
teach_ben_so <- 217.47         #Yearly secondary schooling teacher benefits	217.47
n_students_so <- 45            #Average pupils per teacher	45


#############
##### Notes:
#############
### Source ---->  Input ----> Model ----> Policy Estimates (output)
###  (_so)        (_in)       (_mo)        (_pe)
### values      functions   functions      values
###             & values    & values 
### arguments in functions should used "_var" and functions should "_f"

#invisible( list2env(call_params_f(),.GlobalEnv) )

# on growth_rate_so: (http://data.worldbank.org/indicator/NY.GDP.PCAP.KD/), see calculation on "Kenya GDP per capita" tab. In W@W this equals 1.52%. ISSUE: This growth number should be updated to be 2002-2014, I think.
# on coef_exp_so: 1998/1999 Kenyan labor force survey; regression of earnings on age, age^2, female dummy, indicators for attained primary/secondary/beyond, and province dummies. Estimate used in W@W: (0.1019575, -0.0010413). ISSUE: For now assume no further life cycle adjustment beyond KLPS-3 (likely a conservative assumption).
# coverage_so: Overall Saturation (0.511) / 0.75 - not reported in table, average of T & C
```


# Key policy estimates for policy makers  

```{r final-output}

```

# Methodology

## Main Equation (the model)

\begin{equation}
NPV =  \sum_{\gamma} N_{\gamma} \left[
\tau \sum_{t=0}^{50} \left( \frac{1}{1 + r}\right)^{t} w_{t}
\left( \lambda_{1, \gamma} + \frac{p \lambda_{2, \gamma}}{R} \right) -
K \sum_{t=0}^{50} \left( \frac{1}{1 + r}\right)^{t} \Delta \overline{E}_{\gamma t}(S1,S2)
\right] - \left( S_{2}Q(S_{2}) - S_{1}Q(S_{1}) \right)
\label{eq:1}
\tag{1}
\end{equation}


```{r model} 
# add suffix _var to args
# - inputs: tax_rev_init_mo, top_tax_base_in
# - outputs: total_rev_pe
# Gamma is used to index gender.
npv_mo_f <- function(n_male_var = 1/2, n_female_var = 1/2,
                interest_r_var = interest_r_so,
                wage_var = wage_t_so,
                lambda1_male_var = lambda1_so[1],
                lambda1_female_var = lambda1_so[2],
                tax_var = tax_so,
                saturation_var = saturation_so,             
                coverage_var = coverage_so,
                cost_of_schooling_var = cost_per_student,
                delta_ed_male_var = delta_ed_so[,1],
                delta_ed_female_var = delta_ed_so[,1],
                lambda2_male_var = lambda2_so[1],
                lambda2_female_var = lambda2_so[2],
                s1_var = 0, q1_var = 0, s2_var = s2_so, q2_var = q2_so,
                periods_var = periods_so) {
  ns <- c(n_male_var, n_female_var)
  lambda1s <- c(lambda1_male_var, lambda1_female_var)
  lambda2s <- c(lambda2_male_var, lambda2_female_var)
  index_t <- 0:periods
  delta_ed_s <- cbind(delta_ed_male_var, delta_ed_female_var)
  delta_ed_s <- rbind(c(0,0), delta_ed_s, matrix(0,41, 2) )

  benef <- matrix(NA, 51,2)
  for (i in 1:2){
  benef[,i] <- ( 1 / (1 + interest_r_var) )^index_t * wage_var *
                     ( lambda1s[i] + saturation_var * lambda2s[i] / coverage_var )
  }

  res1 <- sum( ns * ( tax_var * apply(benef, 2, sum) -
            apply( ( 1 / (1 + interest_r_var) )^index_t *
                     delta_ed_s * cost_of_schooling_var, 2, sum) )
          ) - (s2_var * q2_var  - s1_var * q1_var)
#  browser()
  return(res1)  
}
```


## Sub components:

### 1 - "$r$"  

The real interest rate $r$ is obtained from the interest rate on betterment bonds (`r round(gov_bonds_so, 3)`) minus the inflation rate (`r inflation_so`).

```{r interest-rate}
# - inputs: gov_bonds_so, inflation_so
# - outputs: interest_in
interest_in_f <- function(gov_bonds_var = gov_bonds_so , inflation_var = inflation_so) {  
  interest_in = gov_bonds_var - inflation_var 
  return(list("interest_in" = interest_in))
}
invisible( list2env(interest_in_f(),.GlobalEnv) )
```

The resulting value is a $r$ = `r paste(round(100*interest_in,2), "%", sep="")`

### 2 - "$w_{t}$"

\begin{equation}
NPV =  \sum_{\gamma} N_{\gamma} \left[
\tau \sum_{t=0}^{50}\left(  \frac{1}{1 + r}\right)^{t} \blue{ w_{t} }
\left( \lambda_{1, \gamma} + \frac{p \lambda_{2, \gamma}}{R} \right) -
K \sum_{t=0}^{50} \left( \frac{1}{1 + r}\right)^{t} \Delta \overline{E}_{\gamma t}(S1,S2)
\right] - \left( S_{2}Q(S_{2}) - S_{1}Q(S_{1}) \right)
\end{equation}


\begin{equation}
w_t =  \text{#weeks} \times w_0 (1 + g)^{Xp}(1 + \hat{\beta_1} Xp + \hat{\beta_2} Xp^2) \quad \text{for } t=10, \dots, 50
\end{equation}

individual in the data are assumed to enter the labor force 10 years after the (data) present day ($w_t = 0$ for $t<10$). Wage at time $t$ is the weekly starting wage in USD ($w_0$) that has a base growth rate equal to the per capita GDP growth ($g$) applied to however many years of work ($Xp$). In addition to this growth, the salaries are adjusted to represent a (concave) wage life cycle profile ($1 + \hat{\beta_1} Xp + \hat{\beta_2} Xp^2$).

#### 2.1 - "$w_0$"

\begin{equation}
w_t =  \text{#weeks} \times \blue{w_0} (1 + g)^{Xp}(1 + \hat{\beta_1} Xp + \hat{\beta_2} Xp^2)
\end{equation}

\begin{equation}
w_0 = \frac{1}{ex} \sum_{l \in \{ag, ww, se\}}w_{l}\alpha_{l} \\ \quad \text{with: } \alpha_{l}= \frac{ h_{l}}{h_{ag} + h_{ww} + h_{se}}  
\end{equation}

The initial wage in dollars ($w_{0}$) is a weighted average of wages for control group in agriculture, working wage, and self-employed sectors ($ag, ww, se$). The weights correspond to the average number of hours in each sector ($h_l$) relative to the sum of the average number of hours in each sector.

The wage in agriculture comes from research (Suri, 2011), the working wage comes from the data and its defined as  hourly wage for the control group for those who reported more than 10 hrs of work per week. The self-employed wage ($w_{se}$) was constructed as follows:

\begin{equation}
w_{se} =  \frac{ \text{Monthly self-employed profits} }{4.5 \times E[h_{se}|h_{se}>0] }
\end{equation}

Where both parameters (Monthly self-employed profits and self-employed hours for the control group, conditional on hrs >0 - $E[h_{se}|h_{se}>0]$ -) come from the data (ww paper).  The measure of hours in self employment used to compute wages is ($E[h_{se}|h_{se}>0]$) is different from the one is to compute the weights $\alpha_l$ above. The first one captures hours of work among those actively employed in the self-employed sector, and the second one captures the average hours of work in self-employed among all the population of workin age in the sample (hence capturing the relative inportance of the self employed sector in the economy)



```{r wage_t}
experience_in <- 0:periods_so - time_to_jm_so

wage_0_f <- function(wage_ag_var = wage_ag_so,  
                     wage_ww_var = wage_ww_so,
                     profits_se_var = profits_se_so,
                     hours_se_cond_var = hours_se_cond_so,  
                     hours_ag_var = hours_ag_so,
                     hours_ww_var = hours_ww_so,
                     hours_se_var = hours_se_so,
                     ex_rate_var = ex_rate_so) {
  wage_se <- profits_se_var / (4.5 * hours_se_cond_var)
  wage_ls <- c(wage_ag_var, wage_ww_var, wage_se)
  alpha_ls <- c(hours_ag_var, hours_ww_var, hours_se_var) / sum( c(hours_ag_var, hours_ww_var, hours_se_var) )
  res1 <- 1/ex_rate_var * sum( wage_ls * alpha_ls )
  return(res1)
}

#close to value from spreadsheet (Assumps&Panel A Calcs!B137 = 0.1481084),
#but I suspect diff due to computational precision

wage_0_so <- wage_0_f()  

wage_t <- function(wage_0 = wage_0_so,
                   growth_rate = growth_rate_so,
                   experience = experience_in,
                   coef_exp1 = coef_exp_so[1],
                   coef_exp2 = coef_exp_so[2]) {
  res1 <- 52 * wage_0 *( ( 1 + growth_rate )^experience ) *
    ( 1 + coef_exp1 * experience + coef_exp2 * experience^2 ) *
    ifelse(0:periods_so >= time_to_jm_so, 1, 0)
  return(res1)
}

#close to value from spreadsheet (Calcs-Table 5!N21.. = 7.701634678),
#but I suspect diff due to computational precision
wage_t_so <- wage_t()
```



### 3 - "$\lambda_{1,\gamma}$"  and  "$\lambda_{2,\gamma}$"

\begin{equation}
NPV =  \sum_{\gamma} N_{\gamma} \left[
\tau \sum_{t=0}^{50}\left(  \frac{1}{1 + r}\right)^{t} w_{t}
\left(\blue{ \lambda_{1, \gamma} } + \frac{p \blue{\lambda_{2, \gamma}}}{R} \right) -
K \sum_{t=0}^{50} \left( \frac{1}{1 + r}\right)^{t} \Delta \overline{E}_{\gamma t}(S1,S2)
\right] - \left( S_{2}Q(S_{2}) - S_{1}Q(S_{1}) \right)
\end{equation}

$\lambda_{1,\gamma}$ represents the estimated impact of deworming on hours of work for men a women. This two parameter are combined with a underweighted mean:

\begin{equation}
\lambda_{1} = \frac{1}{2} \lambda_{1,male} + \frac{1}{2} \lambda_{1,female}
\end{equation}
Its components come from research (W\@W).

$\lambda_{2,\gamma}$ the estimated externality effect (EXPLAIN) and comes from research (W\@W). Note that this parameter in not estimated by gender, so we repeat its value two times.

```{r lambdas}
# - inputs: gov_bonds_so, inflation_so
# - outputs: interest_in
lambdas_in_f <- function(lambda1_var = lambda1_so, lambda2_var = lambda2_so){
    lambda1_in <- rep(0.5 * lambda1_so[1] + 0.5 *lambda1_so[2], 2)
    lambda2_in <- rep(lambda2_so, 2)
    return(list("lambda1_in" = lambda1_in, "lambda2_in" = lambda2_in))  
}
invisible( list2env(lambdas_in_f(),.GlobalEnv) )
```


### 4 - $R$ and $p$

\begin{equation}
NPV =  \sum_{\gamma} N_{\gamma} \left[
\tau \sum_{t=0}^{50}\left(  \frac{1}{1 + r}\right)^{t} w_{t}
\left( \lambda_{1, \gamma}  + \frac{\blue{p} \lambda_{2, \gamma}}{\blue{R}} \right) -
K \sum_{t=0}^{50} \left( \frac{1}{1 + r}\right)^{t} \Delta \overline{E}_{\gamma t}(S1,S2)
\right] - \left( S_{2}Q(S_{2}) - S_{1}Q(S_{1}) \right)
\end{equation}

The coverage, $R$, is defined as the fraction, among all neighboring schools (within 6 km), that belongs to the treatment group (last paragraph of page 9(1645) of paper). As the treatment was appplied to approximatedly two thirds of the population, $R$ is set to: $R  = `r round(coverage_so, 2)`$.  

*Overall Saturation* is set at `r saturation_so` [ASK TED ABOUT A DEFINITION FOR THIS PARAM]. And $Q(full)$ is the take-up of the treatment with full subsidy, taken from the literature to be at 

The saturation of the intervention, $p$, measures the fraction of the population that is effectively usign the treatment and is defined as:  

\begin{equation}
p = R \times Q(full)  + (1 - R) \times Q(0)
\end{equation}

For this (or similar?) setting Miguel and Kremer 2007 [add page, table, col, row] estimate that there is almost no take-up without subsidy, hence $Q(0)$ is assinged the value of `r q_zero_so`. The same article [add page, table, col, row] estimates that take-up with full subsidy is $Q(full) = `r q_full_so`$.

```{r coverage-and-saturation}
# - inputs: coverage_so, q_full_so, q_zero_so
# - outputs: saturation_in
saturation_in_f <- function(coverage_var = coverage_so, q_full_var = q_full_so, q_zero_var = q_zero_so){
    saturation_in <- coverage_so * q_full_so + ( 1 - coverage_so ) * q_zero_so
    return(list("saturation_in" = saturation_in))
}
invisible( list2env(saturation_in_f(),.GlobalEnv) )
```



### 5 - $K$ and $\Delta \overline{E}_{\gamma t}(S1,S2)$ AQUI VOY

\begin{equation}
NPV =  \sum_{\gamma} N_{\gamma} \left[
\tau \sum_{t=0}^{50}\left(  \frac{1}{1 + r}\right)^{t} w_{t}
\left( \lambda_{1, \gamma}  + \frac{p \lambda_{2, \gamma}}{R} \right) -
\blue{K} \sum_{t=0}^{50} \left( \frac{1}{1 + r}\right)^{t} \blue{ \Delta \overline{E}_{\gamma t}(S1,S2) }
\right] - \left( S_{2}Q(S_{2}) - S_{1}Q(S_{1}) \right)
\end{equation}

$K$ represents the cost per student. This is calculated as the salary of the teacher plus benefits, divided by the average number of students per teacher.

\begin{equation}
K = \frac{\text{teacher salary} + \text{teacher benefits}}{\text{# Students}}
\end{equation}

```{r cost-per-student}
cost_per_student <- (teach_sal_val + teach_ben_val) / n_students_val
```

For $\Delta \overline{E}_{\gamma t}(S1,S2)$ we use a series of estimated effects the additional direct increase in secondary schooling from 1999 to 2007 obtained from [need to define the source "from Joan" in `Assumps&Panel A Calcs!A93`].

This series does not take into account the externality effects. To incorporate the we need another series (same source) that estimates the additional secondary schooling increase due to the externality and add it to the original series.


```{r delta-ed}
# Nothing here yet with delta_ed_vals, but would like to incorporate model from Joan
# delta_ed_vals <-
delta_ed_ext_total <- delta_ed_ext_vals[,1] + delta_ed_vals[,1]
if (FALSE) {
      delta_ed_ext_total_sim <- delta_ed_so_sim[i,] + delta_ed_ext_so_sim[i,]
    if (include_ext_vari==TRUE){
      delta_ed_final <-  delta_ed_ext_total_sim
    }else{
      delta_ed_final <- delta_ed_so_sim[i,]
    }
}
```

**Note:** need to understand better the date of each component (of the model, not only this section).

# Main results
```{r main-results}
#LOAD FIGURE
```


# Montecarlo simulations  
```{r}


# run the model 
#  input: Input vectors for NPV function
#  output: one vector of NPVs (of lenght Nsims)
# Repeat Nsims times
#  input: all functions from above + NSims
#  output: vector of Results of length NSims



#  generate 1 draw of primitive values:
#  inputs: K primitive means and K standard deviations
#  output: K values with one from simulations
one_draw <- function(gov_bonds_var = gov_bonds_so,gov_bonds_sd_var      = 0.1 * gov_bonds_so,         # Data
    inflation_var       = inflation_so      , inflation_sd_var       = 0.1 * inflation_so,      
    wage_ag_var         = wage_ag_so        , wage_ag_sd_var         = 0.1 * wage_ag_so,        
    wage_ww_var         = wage_ww_so        , wage_ww_sd_var         = 0.1 * wage_ww_so,        
    profits_se_var      = profits_se_so     , profits_se_sd_var      = 0.1 * profits_se_so,     
    hours_se_cond_var   = hours_se_cond_so  , hours_se_cond_sd_var   = 0.1 * hours_se_cond_so,  
    hours_ag_var        = hours_ag_so       , hours_ag_sd_var        = 0.1 * hours_ag_so,       
    hours_ww_var        = hours_ww_so       , hours_ww_sd_var        = 0.1 * hours_ww_so,       
    hours_se_var        = hours_se_so       , hours_se_sd_var        = 0.1 * hours_se_so,       
    ex_rate_var         = ex_rate_so        , ex_rate_sd_var         = 0.1 * ex_rate_so,        
    growth_rate_var     = growth_rate_so    , growth_rate_sd_var     = 0.1 * growth_rate_so,    
    coverage_var        = coverage_so       , coverage_sd_var        = 0.1 * coverage_so,       
    tax_var             = tax_so            , tax_sd_var             = 0.1 * tax_so,            
    unit_cost_local_var = unit_cost_local_so, unit_cost_local_sd_var = 0.1 * unit_cost_local_so,
    years_of_treat_var  = years_of_treat_so , years_of_treat_sd_var  = 0.1 * years_of_treat_so,   
    lambda1_var         = lambda1_so       , lambda1_sd_var         = c(0.17, 0.17),                # Research     
    lambda2_var         = lambda2_so        , lambda2_sd_var         = 0.1 * lambda2_so,        
    q_full_var          = q_full_so         , q_full_sd_var          = 0.1 * q_full_so,         
    q_zero_var          = q_zero_so         , q_zero_sd_var          = 0.1 * q_zero_so,         
    delta_ed_var        = 1                  , delta_ed_sd_var        = 1 ,       
    delta_ed_ext_var    = 1                  , delta_ed_ext_sd_var    = 1 ,      
    periods_var         = periods_so        , periods_sd_var         = 0.1 * periods_so,            # Guesswork
    time_to_jm_var      = time_to_jm_so     , time_to_sd_var         = 0.1 * time_to_jm_so,      
    coef_exp_var        = coef_exp_so      , coef_exp_sd_var        = c(0.001 , 0.001),       
    teach_sal_var       = teach_sal_so      , teach_sal_sd_var       = 0.1 * teach_sal_so,       
    teach_ben_var       = teach_ben_so      , teach_ben_sd_var       = 0.1 * teach_ben_so,       
    n_students_var      = n_students_so     , n_students_sd_var      = 0.1 * n_students_so){
    
    rm(list = ls(pattern= "_in") )
    #############
    ##### Data   
    #############
    gov_bonds_in <-           rnorm(1, gov_bonds_var      , gov_bonds_sd_var      ) 
    inflation_in <-           rnorm(1, inflation_var      , inflation_sd_var      ) 
    wage_ag_in <-             rnorm(1, wage_ag_var        , wage_ag_sd_var        )
    wage_ww_in <-             rnorm(1, wage_ww_var        , wage_ww_sd_var        )
    profits_se_in <-          rnorm(1, profits_se_var     , profits_se_sd_var     ) 
    hours_se_cond_in <-       rnorm(1, hours_se_cond_var  , hours_se_cond_sd_var  )
    hours_ag_in <-            rnorm(1, hours_ag_var       , hours_ag_sd_var       ) 
    hours_ww_in <-            rnorm(1, hours_ww_var       , hours_ww_sd_var       )
    hours_se_in <-            rnorm(1, hours_se_var       , hours_se_sd_var       )
    ex_rate_in <-             rnorm(1, ex_rate_var        , ex_rate_sd_var        )
    growth_rate_in <-         rnorm(1, growth_rate_var    , growth_rate_sd_var    )
    coverage_in  <-           rnorm(1, coverage_var       , coverage_sd_var       )
    tax_in <-                 rnorm(1, tax_var            , tax_sd_var            )
    unit_cost_local_in <-     rnorm(1, unit_cost_local_var, unit_cost_local_sd_var)
    years_of_treat_in <-      rnorm(1, years_of_treat_var , years_of_treat_sd_var )
    #############    
    ##### Research 
    #############     
    lambda1_in <-             rnorm(2, lambda1_var       , lambda1_sd_var        ) 
    lambda2_in <-             rnorm(1, lambda2_var       , lambda2_sd_var        )
    q_full_in <-              rnorm(1, q_full_var        , q_full_sd_var         )
    q_zero_in <-              rnorm(1, q_zero_var        , q_zero_sd_var         )
    delta_ed_in <-            rnorm(1, delta_ed_var      , delta_ed_sd_var * sd(delta_ed_so[,1])) * delta_ed_so[,1] 
    delta_ed_ext_in <-        rnorm(1, delta_ed_ext_var  , delta_ed_ext_sd_var * sd(delta_ed_ext_so[,1])) * delta_ed_ext_so[,1] 
    #############
    ##### Guess work    
    ############# 
    periods_in <-            rnorm(1, periods_var        , periods_sd_var     )
    time_to_jm_in <-         rnorm(1, time_to_jm_var     , time_to_sd_var     )
    coef_exp_in <-           rnorm(2, coef_exp_var       , coef_exp_sd_var    )
    teach_sal_in <-          rnorm(1, teach_sal_var      , teach_sal_sd_var   )
    teach_ben_in <-          rnorm(1, teach_ben_var      , teach_ben_sd_var   )
    n_students_in <-         rnorm(1, n_students_var     , n_students_sd_var  )
    #############
    return( sapply( ls(pattern= "_in"), function(x) get(x)) ) 
    }
#asd <- one_draw()
# Takes each element of list and assings it an object with the same name
#list2env(asd,.GlobalEnv)
# compute the elements of the model
#  input: K vectors with draws from sims
#  output: Input vectors for NPV function

one_draw_so <- one_draw()

elements <- function(inputs = one_draw_so) {
    list2env(inputs,.GlobalEnv)
    # 1 - "r""
    interest_r_var <- interest_var_comp(gov_bonds_in, inflation_in)
    return(interest_r_var)
}   
elements()

if (FALSE) {
  # - Model
  npv_sim <- rep(NA, nsims)
  #yes externality NPV
    # 1 - "r""
    interst_r_so <- gov_bonds_sim[i] - inflation_sim[i]
    interest_r_var <- interest_var_comp(gov_bonds_in, inflation_in)
    # 2 - "w_t"
    wage_0_so <- wage_0_f(wage_ag = wage_ag_so_sim[i],
                           wage_ww = wage_ww_so_sim[i],
                           profits_se = profits_se_so_sim[i],
                           hours_se_cond = hours_se_cond_so_sim[i],
                           hours_ag = hours_ag_so_sim[i],
                           hours_ww = hours_ww_so_sim[i],
                           hours_se = hours_se_so_sim[i],
                           ex_rate = ex_rate_so_sim[i])  
    experience_so <- 0:periods_so - time_to_jm_so
    wage_t_so <- wage_t(wage_0 = wage_0_so,
                         growth_rate = growth_rate_so_sim[i],
                         experience = experience_so,
                         coef_exp1 = coef_exp_so_sim[i,1],
                         coef_exp2 = coef_exp_so_sim[i,2])
    # 3 - “λ1,γ” and “λ2,γ”
    lambda1_so_aux <- rep(0.5 * lambda1_so_sim[i,1] + 0.5 * lambda1_so_sim[i,2], 2)
    lambda2_so <- rep(lambda2_so_sim[i], 2)
    # 4 - R and p
    #coverage_so_aux <-  saturation_so_sim[i] / full_saturation_so_sim[i]
    #saturation_so_aux <- full_saturation_so_sim[i] * coverage_so_sim[i]
    # 5 - K and ΔE⎯⎯⎯⎯γt(S1,S2)
    cost_per_student <- (teach_sal_so_sim[i] + teach_ben_so_sim[i]) / n_students_so_sim[i]
    delta_ed_ext_total_sim <- delta_ed_so_sim[i,] + delta_ed_ext_so_sim[i,]
    if (include_ext_vari==TRUE){
      delta_ed_final <-  delta_ed_ext_total_sim
    }else{
      delta_ed_final <- delta_ed_so_sim[i,]
    }

    #6 - (S2Q(S2)−S1Q(S1))
    q2_so_aux <- q_full_so_sim[i]
    s2_so_aux <- ( unit_cost_local_so_sim[i] / ex_rate_so_sim[i] ) * years_of_treat_so_sim[i]
 
}
  


    ```

# Sensitivity Analysis  
