---
title: "Dynamic Document for Fiscal Impacts of Deworming"
author: ""
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: latex_fragment
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
editor_options: 
  chunk_output_type: console
---

```{r, include=F}
rm(list = ls())
options(tinytex.verbose = TRUE)
```

```{r setup, include=FALSE} 
# Loading required libraries
list.of.packages <- c("tidyverse", "haven", "here", "kableExtra")

lapply(list.of.packages, library, character.only = TRUE)
library(rootSolve)
knitr::opts_knit$set(root.dir = here())
knitr::opts_chunk$set(echo = F)

print_code <- TRUE
``` 

```{r parameters}

# TO-DO:
# add source links to bonds and inflation
# get rid of gamma in the function
# edit methodology section
# get rid of .02. take sum of vector instead of mean and refer to Baird et. al.
# change code of equations to match new setup
# insert figures
# format table

# TIME-VARIANT INPUTS (may need to be updated)

  # Data  
    gov_bonds_so <- 0.09                   # Interest rate on government bonds - trading economics (updated 10/14) (add links)
    inflation_so <- 0.04                   # Kenyan inflation rate - World Bank Development Indicators (updated 10/14) (add links)
    tax_so       <- 0.16575                # ADD INFO!
    unit_cost_so <- 0.42                   # Unit cost of deworming (in 2018 USD) - from Evidence Action
  # unit_cost_local_so <- 43.66            #Deworm the World
    
  # Research
    lambda1_2017usdppp_so <- c(79.51465,   # avg treatment effect from klps2-4 pooled (already adjusted for ppp and inflation) - w@w
                               79.51465,   # avg treatment effect from klps2-4 pooled (already adjusted for ppp and inflation) - w@w 
                               79.51465)   # avg treatment effect from klps2-4 pooled (already adjusted for ppp and inflation) - w@w
    consump_2017usdppp_so <- c(0,          # avg treatment effect from klps2 not collected (treat as if zero)
                               305.108,  # avg treatment effect from klps3-4 pooled (already adjusted for ppp and inflation) - w@w 
                               305.108)   # avg treatment effect from klps3-4 pooled (already adjusted for ppp and inflation) - w@w
    wtp_so <- 50*12                        # willingness to pay for deworming medication (2018 KSH)- Health-WTP_2018-01-19.pdf
    
  # Guess work   
    periods_so    <- 50                    #Total number of periods to forecast wages
    time_to_jm_so <- 10                    #Time from intial period until individual join the labor force
    teach_sal_so  <- 50000                 #Monthly secondary schooling compensation	(in 2017 KES) overestimated to account for benefits - news sources
                                              # https://www.tuko.co.ke/287766-secondary-school-teachers-salary-kenya.html
                                              # https://www.standardmedia.co.ke/article/2001249581/windfall-for-teachers-as-tsc-releases-new-salaries
    teach_sal_so <- 12*teach_sal_so        #Yearly secondary schooling compensation
    n_students_so <- 45                    #Average pupils per teacher	45

# TIME-INVARIANT INPUTS
  
  # Data 
    years_of_treat_so <- 2.41       # Additional Years of Treatment - Table 1, Panel A
    
    ex_rate_2018        <-101.30    # Exchange rate (KES per international $) - https://data.worldbank.org/indicator/PA.NUS.FCRF?locations=KE
    ex_rate_2009        <- 77.352   # Exchange rate (KES per international $) - https://data.worldbank.org/indicator/PA.NUS.FCRF?locations=KE
    ex_rate_2007        <- 67.318   # Exchange rate (KES per international $) - https://data.worldbank.org/indicator/PA.NUS.FCRF?locations=KE
    ex_rate_2018_ppp_so <- 50.058   # KLPS4_E+_globals.do (originally from the World Bank)
    ex_rate_2017_ppp_so <- 49.773   # KLPS4_E+_globals.do (originally from the World Bank)
    ex_rate_2009_ppp_so <- 31.317   # KLPS4_E+_globals.do (originally from the World Bank)
    ex_rate_2007_ppp_so <- 25.024   # KLPS4_E+_globals.do (originally from the World Bank)
    
    cpi_2007_so <- 207.342          # KLPS4_E+_globals.do (originally from the Bureau of Labor Statistics)
    cpi_2009_so <- 214.537          # KLPS4_E+_globals.do (originally from the Bureau of Labor Statistics)
    cpi_2018_so <- 251.10           # KLPS4_E+_globals.do (originally from the Bureau of Labor Statistics)
    cpi_2017_so <- 245.120          # KLPS4_E+_globals.do (originally from the Bureau of Labor Statistics)
    
  # Research
    q_full_so   <- 0.75                     #Take up rates with full subsidy. From Miguel and Kremmer (2007)
    q_zero_so   <- 0                        #Take up rates with zero subsidy. From Miguel and Kremmer (2007)
    delta_ed_so <- c(-0.00176350949079451,  # (Delta E) Additional direct seconday schooling increase (from Joan)
                      0.00696052250263997, 
                      0.0258570306763183,     
                      0.0239963665555466,  
                      0.027301406306074,   
                      0.0234125454594173,
                      0.0279278879439199,  
                      0.00647044449446303, 
                      0.00835739437790601)                                     
    delta_ed_so <- cbind(delta_ed_so, 1999:2007)

# CALCULATIONS TO CONVERT ALL CURRENCY TO 2017 USD PPP (will need to be updated if monetary inputs are updated)
    
  # Adjust for currency: convert all costs to USD PPP **NOTE: 1 international dollar = 1 USD (https://data.worldbank.org/indicator/PA.NUS.PRVT.PP?locations=KE-US)***
      
    unit_cost_ppp_so <- unit_cost_so*ex_rate_2018/ex_rate_2018_ppp_so
    teach_sal_ppp_so <- teach_sal_so/ex_rate_2017_ppp_so
    wtp_so           <- wtp_so/ex_rate_2018_ppp_so
    
  # Adjust for inflation: convert all costs to 2017 USD
    
    unit_cost_2017usdppp_so <- unit_cost_ppp_so*cpi_2017_so/cpi_2018_so
    teach_sal_2017usdppp_so <- teach_sal_ppp_so*cpi_2017_so/cpi_2017_so # redundant, but for the sake of consistency
    wtp_2017usdppp_so       <- wtp_so*cpi_2017_so/cpi_2018_so

#############
##### Notes:
#############
### Source ---->  Input ----> Model ----> Policy Estimates (output)
###  (_so)        (_in)       (_mo)        (_pe)
### values      functions   functions      values
###             & values    & values 
### arguments in functions should used "_var" and functions should "_f"

```

```{r model} 
# add suffix _var to args 
# - inputs: tax_rev_init_mo, top_tax_base_in  
# - outputs: total_rev_pe 
npv_mo_f <- function(interest_r_var = interest_in,
                n_male_var = 1/2, n_female_var = 1/2, 
                delta_welfare_var,
                tax_var = tax_so,
                cost_of_schooling_var = cost_per_student_in,
                delta_ed_male_var = delta_ed_so[,1],
                delta_ed_female_var = delta_ed_so[,1],
                s1_var = 0, q1_var = 0, s2_var = s2_in, q2_var = q2_in,
                periods_var = periods_so, years_of_treat_var = years_of_treat_so) {
  ns <- c(n_male_var, n_female_var)
  l_index_t <- 0:periods_var
  delta_ed_s <- cbind(delta_ed_male_var, delta_ed_female_var) 
  delta_ed_s <- rbind(c(0,0), delta_ed_s, matrix(0,41, 2) )
############################################################################### 
  benef <- matrix(NA, 51,2)
  for (i in 1:2){
  benef[,i] <- ( 1 / (1 + interest_r_var) )^l_index_t * delta_welfare_var
  }

  res1 <- sum( ns * ( tax_var * apply(benef, 2, sum) -
          apply( ( 1 / (1 + interest_r_var) )^l_index_t *
                     delta_ed_s * cost_of_schooling_var, 2, sum) )) - 
          sum( ( 1 / (1 + interest_r_var) )^(0:2) * (s2_var * q2_var  - s1_var * q1_var) )
############################################################################### 
  return(res1) 
}
```

```{r interest-rate} 
# - inputs: gov_bonds_so, inflation_so
# - outputs: interest_in
interest_in_f <- function(gov_bonds_var = gov_bonds_so , inflation_var = inflation_so) {  
############################################################################### 
  interest_in = gov_bonds_var - inflation_var 
############################################################################### 
  return(list("interest_in" = interest_in))
}
invisible( list2env(interest_in_f(),.GlobalEnv) )
```

```{r costs}
# - inputs: 
# - outputs: 
costs_f <- function(unit_cost_var = unit_cost_2017usdppp_so,
                    years_of_treat_var = years_of_treat_so, 
                    q_full_var = q_full_so){
############################################################################### 
    s2_in <- c(rep(unit_cost_var,2), .4*unit_cost_var)
    q2_in <- q_full_var
############################################################################### 
    return(list("s2_in" = s2_in, "q2_in" = q2_in)) 
} 
invisible( list2env(costs_f(),.GlobalEnv) )


```

```{r ed-costs}

# - inputs: coverage_so, q_full_so, q_zero_so 
# - outputs: saturation_in 
ed_costs_in_f <- function(teach_sal_var = teach_sal_2017usdppp_so, 
                          n_students_var = n_students_so,
                          delta_ed_var = delta_ed_so[,1]){
 ###############################################################################    
    cost_per_student_in <- (teach_sal_var)/ n_students_var
    delta_ed_in <- delta_ed_var
############################################################################### 
    return(list("cost_per_student_in" = cost_per_student_in, "delta_ed_in" = delta_ed_in)) 
} 
invisible( list2env(ed_costs_in_f(),.GlobalEnv) )
```

```{r delta_earnings, eval=TRUE}
# - inputs: periods_so, lambda1_2017usdppp_so
# - outputs: 
delta_welfare_in_f <- function(t_var = 0:periods_so, 
                               welfarek1_var, 
                               welfarek2_var, 
                               welfarek3_var) {
############################################################################### 
delta_welfare_in <- 1*(10 <= t_var & t_var < 15) * welfarek1_var + 
                    1*(15 <= t_var & t_var < 20) * welfarek2_var + 
                    1*(20 <= t_var & t_var < 25) * welfarek3_var
############################################################################### 
  return(delta_welfare_in)
}
``` 

```{r delta_earnings_p, eval=TRUE}
# - inputs: periods_so, lambda1_2017usdppp_so
# - outputs: 
delta_welfare_p_in_f <- function(t_var = 0:periods_so, 
                                  welfarek1_var, 
                                  welfarek2_var, 
                                  welfarek3_var) {
############################################################################### 
delta_welfare_p_in <- 1*(10 <= t_var & t_var < 15) * welfarek1_var + 
                      1*(15 <= t_var & t_var < 20) * welfarek2_var + 
                      1*(20 <= t_var) * welfarek3_var
############################################################################### 
  return(delta_welfare_p_in)
}
``` 

```{r earnings, eval=TRUE}

delta_earnings_in = delta_welfare_in_f(welfarek1_var = lambda1_2017usdppp_so[1],
                                       welfarek2_var = lambda1_2017usdppp_so[2],
                                       welfarek3_var = lambda1_2017usdppp_so[3])

delta_earnings_p_in = delta_welfare_p_in_f(welfarek1_var = lambda1_2017usdppp_so[1],
                                           welfarek2_var = lambda1_2017usdppp_so[2],
                                           welfarek3_var = lambda1_2017usdppp_so[3])
```

```{r consumption, eval=TRUE}

delta_consumption_in = delta_welfare_in_f(welfarek1_var = consump_2017usdppp_so[1],
                                          welfarek2_var = consump_2017usdppp_so[2],
                                          welfarek3_var = consump_2017usdppp_so[3])

delta_consumption_p_in = delta_welfare_p_in_f(welfarek1_var = consump_2017usdppp_so[1],
                                              welfarek2_var = consump_2017usdppp_so[2],
                                              welfarek3_var = consump_2017usdppp_so[3])
```

```{r model_cwelfare earnings}
# welfare function for earnings, 50 year(persist)
npv_cwelfare_p_mo_f <- function(interest_r_var = interest_in,
                n_male_var = 1/2, n_female_var = 1/2, 
                delta_welfare_var,
                lambda1_male_var = lambda1_2017usdppp_so[1],
                lambda1_female_var = lambda1_2017usdppp_so[2], 
                tax_var = tax_so,
                cost_of_schooling_var = cost_per_student_in,
                delta_ed_male_var = delta_ed_so[,1],
                delta_ed_female_var = delta_ed_so[,1],
                s1_var = 0, q1_var = 0, s2_var = s2_in, q2_var = q2_in,
                periods_var = periods_so, years_of_treat_var = years_of_treat_so) {
  ns <- c(n_male_var, n_female_var)
  l_index_t <- 0:periods_var
  delta_ed_s <- cbind(delta_ed_male_var, delta_ed_female_var) 
  delta_ed_s <- rbind(c(0,0), delta_ed_s, matrix(0,41, 2) )
############################################################################### 
  benef <- matrix(NA, 51,2)
  for (i in 1:2){
  benef[,i] <- ( 1 / (1 + interest_r_var) )^l_index_t * (1*(10 <= l_index_t & l_index_t < 15) * delta_welfare_var + 1*(15 <= l_index_t & l_index_t < 20) * delta_welfare_var +1*(20 <= l_index_t) * delta_welfare_var)
  }

  res1 <- sum( ns * ( tax_var * apply(benef, 2, sum) -
            apply( ( 1 / (1 + interest_r_var) )^l_index_t *
                     delta_ed_s * cost_of_schooling_var, 2, sum) )) - 
    sum( ( 1 / (1 + interest_r_var) )^(0:2) * (s2_var * q2_var  - s1_var * q1_var) )
############################################################################### 
  return(res1) 
}

# welfare function for earnings, 25 year (die)
npv_cwelfare_d_mo_f <- function(interest_r_var = interest_in,
                n_male_var = 1/2, n_female_var = 1/2, 
                delta_welfare_var,
                lambda1_male_var = lambda1_2017usdppp_so[1],
                lambda1_female_var = lambda1_2017usdppp_so[2], 
                tax_var = tax_so,
                cost_of_schooling_var = cost_per_student_in,
                delta_ed_male_var = delta_ed_so[,1],
                delta_ed_female_var = delta_ed_so[,1],
                s1_var = 0, q1_var = 0, s2_var = s2_in, q2_var = q2_in,
                periods_var = periods_so, years_of_treat_var = years_of_treat_so) {
  ns <- c(n_male_var, n_female_var)
  l_index_t <- 0:periods_var
  delta_ed_s <- cbind(delta_ed_male_var, delta_ed_female_var) 
  delta_ed_s <- rbind(c(0,0), delta_ed_s, matrix(0,41, 2) )
############################################################################### 
  benef <- matrix(NA, 51,2)
  for (i in 1:2){
  benef[,i] <- ( 1 / (1 + interest_r_var) )^l_index_t * (1*(10 <= l_index_t & l_index_t < 15) * delta_welfare_var + 1*(15 <= l_index_t & l_index_t < 20) * delta_welfare_var + 1*(20 <= l_index_t & l_index_t < 25) * delta_welfare_var)
  }

  res1 <- sum( ns * ( tax_var * apply(benef, 2, sum) -
            apply( ( 1 / (1 + interest_r_var) )^l_index_t * delta_ed_s * cost_of_schooling_var, 2, sum) )
          ) - sum( ( 1 / (1 + interest_r_var) )^(0:2) * (s2_var * q2_var  - s1_var * q1_var) )
############################################################################### 
  return(res1) 
}
```

```{r model_cwelfare consumption}
# welfare function for consumption, 15-50 year(persist)
npv_cwelfare_p_mo_f_c <- function(interest_r_var = interest_in,
                n_male_var = 1/2, n_female_var = 1/2, 
                delta_welfare_var,
                lambda1_male_var = lambda1_2017usdppp_so[1],
                lambda1_female_var = lambda1_2017usdppp_so[2], 
                tax_var = tax_so,
                cost_of_schooling_var = cost_per_student_in,
                delta_ed_male_var = delta_ed_so[,1],
                delta_ed_female_var = delta_ed_so[,1],
                s1_var = 0, q1_var = 0, s2_var = s2_in, q2_var = q2_in,
                periods_var = periods_so, years_of_treat_var = years_of_treat_so) {
  ns <- c(n_male_var, n_female_var)
  l_index_t <- 0:periods_var
  delta_ed_s <- cbind(delta_ed_male_var, delta_ed_female_var) 
  delta_ed_s <- rbind(c(0,0), delta_ed_s, matrix(0,41, 2) )
############################################################################### 
  benef <- matrix(NA, 51,2)
  for (i in 1:2){
  benef[,i] <-  ( 1 / (1 + interest_r_var) )^l_index_t *(1*(15 <= l_index_t & l_index_t < 20) * delta_welfare_var +1*(20 <= l_index_t) * delta_welfare_var)
  }

  res1 <- sum( ns * ( tax_var * apply(benef, 2, sum) -
            apply( ( 1 / (1 + interest_r_var) )^l_index_t *
                     delta_ed_s * cost_of_schooling_var, 2, sum) )) - 
    sum( ( 1 / (1 + interest_r_var) )^(0:2) * (s2_var * q2_var  - s1_var * q1_var) )
############################################################################### 
  return(res1) 
}

# welfare function for consumptions, 15-25 year(die)
npv_cwelfare_d_mo_f_c <- function(interest_r_var = interest_in,
                n_male_var = 1/2, n_female_var = 1/2, 
                delta_welfare_var,
                lambda1_male_var = lambda1_2017usdppp_so[1],
                lambda1_female_var = lambda1_2017usdppp_so[2], 
                tax_var = tax_so,
                cost_of_schooling_var = cost_per_student_in,
                delta_ed_male_var = delta_ed_so[,1],
                delta_ed_female_var = delta_ed_so[,1],
                s1_var = 0, q1_var = 0, s2_var = s2_in, q2_var = q2_in,
                periods_var = periods_so, years_of_treat_var = years_of_treat_so) {
  ns <- c(n_male_var, n_female_var)
  l_index_t <- 0:periods_var
  delta_ed_s <- cbind(delta_ed_male_var, delta_ed_female_var) 
  delta_ed_s <- rbind(c(0,0), delta_ed_s, matrix(0,41, 2) )
############################################################################### 
  benef <- matrix(NA, 51,2)
  for (i in 1:2){
  benef[,i] <- ( 1 / (1 + interest_r_var) )^l_index_t *(1*(15 <= l_index_t & l_index_t < 20) * delta_welfare_var + 1*(20 <= l_index_t & l_index_t < 25) * delta_welfare_var)
  }

  res1 <- sum( ns * ( tax_var * apply(benef, 2, sum) -
            apply( ( 1 / (1 + interest_r_var) )^l_index_t * delta_ed_s * cost_of_schooling_var, 2, sum) )
          ) - sum( ( 1 / (1 + interest_r_var) )^(0:2) * (s2_var * q2_var  - s1_var * q1_var) )
############################################################################### 
  return(res1) 
}
```

```{r table 1 results}
#Earnings
#########
# PANEL A
#########

e_social_persist_int10 <- (multiroot(function(x) npv_cwelfare_p_mo_f(delta_welfare_var = x, tax_var = 1, interest_r_var = 0.10), 4, maxiter=1000000, positive = T))$root
e_social_persist_int05 <- (multiroot(function(x) npv_cwelfare_p_mo_f(delta_welfare_var = x, tax_var = 1, interest_r_var = 0.05), 4, maxiter=1000000, positive = T))$root
e_social_die_int10     <- (multiroot(function(x) npv_cwelfare_d_mo_f(delta_welfare_var = x, tax_var = 1, interest_r_var = 0.10), 4, maxiter=1000000, positive = T))$root
e_social_die_int05     <- (multiroot(function(x) npv_cwelfare_d_mo_f(delta_welfare_var = x, tax_var = 1, interest_r_var = 0.05), 4, maxiter=1000000, positive = T))$root

e_tax_persist_int10 <- (multiroot(function(x) npv_cwelfare_p_mo_f(delta_welfare_var = x, interest_r_var = 0.10), 4, maxiter=10000000, positive = T))$root
e_tax_persist_int05 <- (multiroot(function(x) npv_cwelfare_p_mo_f(delta_welfare_var = x, interest_r_var = 0.05), 4, maxiter=10000000, positive = T))$root
e_tax_die_int10     <- (multiroot(function(x) npv_cwelfare_d_mo_f(delta_welfare_var = x, interest_r_var = 0.10), 4, maxiter=10000000, positive = T))$root
e_tax_die_int05     <- (multiroot(function(x) npv_cwelfare_d_mo_f(delta_welfare_var = x, interest_r_var = 0.05), 4, maxiter=10000000, positive = T))$root

#Earnings
#########
# PANEL B
#########

# Net Present Value (2017 USD PPP)
e_npv_int05_persist <- npv_mo_f(delta_welfare_var = delta_earnings_p_in, tax_var = 1)
e_npv_int05_die     <- npv_mo_f(delta_welfare_var = delta_earnings_in, tax_var = 1)
e_npv_int10_persist <- npv_mo_f(delta_welfare_var = delta_earnings_p_in, interest_r_var = 0.10, tax_var = 1)
e_npv_int10_die     <- npv_mo_f(delta_welfare_var = delta_earnings_in, interest_r_var = 0.10, tax_var = 1)

# Net Present Value of tax revenue (2017 USD PPP)
e_tax_int05_persist <- npv_mo_f(delta_welfare_var = delta_earnings_p_in, interest_r_var = .05)
e_tax_int05_die     <- npv_mo_f(delta_welfare_var = delta_earnings_in, interest_r_var = .05)
e_tax_int10_persist <- npv_mo_f(delta_welfare_var = delta_earnings_p_in, interest_r_var = 0.10)
e_tax_int10_die     <- npv_mo_f(delta_welfare_var = delta_earnings_in, interest_r_var = 0.10)

#Earnings
#########
# PANEL C
#########

e_irr_social_persist <- (multiroot(function(x) npv_mo_f(interest_r_var = x, tax_var = 1, delta_welfare_var = delta_earnings_p_in), .1, maxiter=1000000, positive = T))$root
e_irr_social_die     <- (multiroot(function(x) npv_mo_f(interest_r_var = x, tax_var = 1, delta_welfare_var = delta_earnings_in), .1, maxiter=10000000, positive = T))$root
e_irr_tax_persist    <- (multiroot(function(x) npv_mo_f(interest_r_var = x, delta_welfare_var = delta_earnings_p_in), .1, maxiter=1000000, positive = T))$root
e_irr_tax_die        <- (multiroot(function(x) npv_mo_f(interest_r_var = x, delta_welfare_var = delta_earnings_in), .1, maxiter=1000000, positive = T))$root

#Consumption
#########
# PANEL A
#########

c_social_persist_int10 <- (multiroot(function(x) npv_cwelfare_p_mo_f_c(delta_welfare_var = x, tax_var = 1, interest_r_var = 0.10), 4, maxiter=1000000, positive = T))$root
c_social_persist_int05 <- (multiroot(function(x) npv_cwelfare_p_mo_f_c(delta_welfare_var = x, tax_var = 1, interest_r_var = 0.05), 4, maxiter=1000000, positive = T))$root
c_social_die_int10     <- (multiroot(function(x) npv_cwelfare_d_mo_f_c(delta_welfare_var = x, tax_var = 1, interest_r_var = 0.10), 4, maxiter=1000000, positive = T))$root
c_social_die_int05     <- (multiroot(function(x) npv_cwelfare_d_mo_f_c(delta_welfare_var = x, tax_var = 1, interest_r_var = 0.05), 4, maxiter=1000000, positive = T))$root

c_tax_persist_int10 <- (multiroot(function(x) npv_cwelfare_p_mo_f_c(delta_welfare_var = x, interest_r_var = 0.10), 4, maxiter=1000000, positive = T))$root
c_tax_persist_int05 <- (multiroot(function(x) npv_cwelfare_p_mo_f_c(delta_welfare_var = x, interest_r_var = 0.05), 4, maxiter=1000000, positive = T))$root
c_tax_die_int10     <- (multiroot(function(x) npv_cwelfare_d_mo_f_c(delta_welfare_var = x, interest_r_var = 0.10), 4, maxiter=1000000, positive = T))$root
c_tax_die_int05     <- (multiroot(function(x) npv_cwelfare_d_mo_f_c(delta_welfare_var = x, interest_r_var = 0.05), 4, maxiter=1000000, positive = T))$root

#Consumption
#########
# PANEL B
#########

# Net Present Value (2017 USD PPP)
c_npv_int05_persist <- npv_mo_f(delta_welfare_var = delta_consumption_p_in, interest_r_var = 0.05, tax_var = 1)
c_npv_int05_die     <- npv_mo_f(delta_welfare_var = delta_consumption_in,   interest_r_var = 0.05, tax_var = 1)
c_npv_int10_persist <- npv_mo_f(delta_welfare_var = delta_consumption_p_in, interest_r_var = 0.10, tax_var = 1)
c_npv_int10_die     <- npv_mo_f(delta_welfare_var = delta_consumption_in,   interest_r_var = 0.10, tax_var = 1)

# Net Present Value of tax revenue (2017 USD PPP)
c_tax_int05_persist <- npv_mo_f(delta_welfare_var = delta_consumption_p_in, interest_r_var = 0.05)
c_tax_int05_die     <- npv_mo_f(delta_welfare_var = delta_consumption_in,   interest_r_var = 0.05)
c_tax_int10_persist <- npv_mo_f(delta_welfare_var = delta_consumption_p_in, interest_r_var = 0.10)
c_tax_int10_die     <- npv_mo_f(delta_welfare_var = delta_consumption_in,   interest_r_var = 0.10)

#Consumption
#########
# PANEL C
#########

c_irr_social_persist <- (multiroot(function(x) npv_mo_f(interest_r_var = x, tax_var = 1, delta_welfare_var = delta_consumption_p_in), .1, maxiter=1000000, positive = T))$root
c_irr_social_die     <- (multiroot(function(x) npv_mo_f(interest_r_var = x, tax_var = 1, delta_welfare_var = delta_consumption_in), .1, maxiter=1000000, positive = T))$root
c_irr_tax_persist    <- (multiroot(function(x) npv_mo_f(interest_r_var = x, delta_welfare_var = delta_consumption_p_in), .1, maxiter=1000000, positive = T))$root
c_irr_tax_die        <- (multiroot(function(x) npv_mo_f(interest_r_var = x, delta_welfare_var = delta_consumption_in), .1, maxiter=1000000, positive = T))$root

```


\begin{table}[H]
\centering
\begin{tabular}{lcccc}
\toprule  
&  \multicolumn{2}{c}{Consumption}
&  \multicolumn{2}{c}{Earnings}	                                    
\\ \cmidrule{2-3} 
\cmidrule{4-5}
& 25 years		  & 50 years	                                        & 25 years 	    & 50 years   
\\
\midrule
 \multicolumn{5}{l}{\textit{Panel A: Required Labor Market Gains (Calculated) for Internal Rates of Return (IRR)}} \\ 
Social IRR of 10\%				           
& `r round(c_social_die_int10,2)`     
& `r format(round(c_social_persist_int10,2), nsmall=2)`  
& `r round(e_social_die_int10,2)`     
& `r format(round(e_social_persist_int10,2), nsmall=2)` \\
Social IRR of 5\% 		     		       
& `r round(c_social_die_int05,2)`     
& `r format(round(c_social_persist_int05,2), nsmall=2)`   
& `r round(e_social_die_int05,2)`     
& `r format(round(e_social_persist_int05,2), nsmall=2)` \\
Fiscal IRR of 10\%       
& `r round(c_tax_die_int10,2)`        
& `r format(round(c_tax_persist_int10,2), nsmall=2)` 	 
& `r round(e_tax_die_int10,2)`        
& `r format(round(e_tax_persist_int10,2), nsmall=2)`  \\
Fiscal IRR of 5\%        
& `r round(c_tax_die_int05,2)`        
& `r format(round(c_tax_persist_int05,2), nsmall=2)`
& `r round(e_tax_die_int05,2)`        
& `r format(round(e_tax_persist_int05,2), nsmall=2)` 	 \\
\multicolumn{5}{l}{\textit{Panel B: Net Present Value (NPV) from Observed Labor Market Gains}} \\
Social NPV for assumed discount rate of 10\%			                 
& `r format(round(c_npv_int10_die,2),nsmall=2)`	       
& `r format(round(c_npv_int10_persist,2),nsmall=2)`	
& `r format(round(e_npv_int10_die,2),nsmall=2)`	       
& `r format(round(e_npv_int10_persist,2),nsmall=2)`  \\
Social NPV for assumed discount rate of 5\% 	 	       
& `r format(round(c_npv_int05_die,2),nsmall=2)`	       
& `r format(round(c_npv_int05_persist,2),nsmall=2)` 
& `r format(round(e_npv_int05_die,2),nsmall=2)`	       
& `r format(round(e_npv_int05_persist,2),nsmall=2)` \\
Fiscal NPV for assumed discount rate of 10\% 
& `r format(round(c_tax_int10_die,2),nsmall=2)`	       
& `r format(round(c_tax_int10_persist,2),nsmall=2)`		 
& `r format(round(e_tax_int10_die,2),nsmall=2)`	       
& `r format(round(e_tax_int10_persist,2),nsmall=2)`  \\
Fiscal NPV for assumed discount rate of 5\%  
& `r format(round(c_tax_int05_die,2),nsmall=2)`	       
& `r format(round(c_tax_int05_persist,2),nsmall=2)`  
& `r format(round(e_tax_int05_die,2),nsmall=2)`	       
& `r format(round(e_tax_int05_persist,2),nsmall=2)`  \\
\multicolumn{5}{l}{\textit{Panel C: Internal Rate of Return (IRR) from Observed Labor Market Gains}}  \\ 
Social IRR 							                   
& `r round(100*c_irr_social_die,1)`\% 
& `r round(100*c_irr_social_persist,1)`\%  
& `r round(100*e_irr_social_die,1)`\% 
& `r round(100*e_irr_social_persist,1)`\%  \\
Fiscal IRR						             
& `r round(100*c_irr_tax_die,1)`\%    
& `r format(round(100*c_irr_tax_persist,1), nsmall=1)`\%  
& `r round(100*e_irr_tax_die,1)`\%    
& `r round(100*e_irr_tax_persist,1)`\%   \\
\bottomrule
\end{tabular}

\end{table}

